Gender Dynamics in Academia: Analyzing Regrade Requests and Course Load Trends, 2010-2016

### 2024-02-14 outputs/paper/paper.qmd
finalize paper

---
title: "Gender Dynamics in Academia: Analyzing Regrade Requests and Course Load Trends, 2010-2016"
subtitle: "A replication of Li and Zahar;"
author: Faiza Imam, Quang Mai & Catherine Punnoose 
thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git, DOI: 10.1257/pol.20210053"
date: today
date-format: long
abstract: "Academia is a complex ecosystem that feeds off a network of social, cultural and innovative influences which often, stem beyond societal norms. This paper replicates the gender implications regarding results in college students and explores potential fluctuations in request patterns over a semester by specifically analyzing the number of classes taken by students and their willingness to submit a grade request throughout the semester. Our results show that there is a trend for female students to submit regrade requests while taking fewer courses compared to a higher course load. Female students experienced grade increases (3%) compared to their male counterparts. We call for further investigation around this topic to understand gender disparities within the world of academia. "
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Gender Dynamics in Academia: Analyzing Regrade Requests and Course Load Trends, 2010-2016"
subtitle: "A replication of Li and Zahar;"
author: Faiza Imam, Quang Mai & Catherine Punnoose 
thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git, DOI: 10.1257/pol.20210053"
date: today
date-format: long
abstract: "Institutionalized and traditional, academia often exacerbates gender differences. This paper then replicates the gender implications behind regrade requests of undergraduate students in Colorado State University from 2010-2016. By analyzing the number of classes taken by students, their willingness to request regrade and actual grade changes, this paper explores fluctuations in regrade request patterns throughout the semester. Our results show that on average males students are more likely to submit regrade requests, and-even when they request regrade for more courses-still have better grade changes compared to female students. We thus call for further investigation around this topic to understand gender disparities within the world of academia. "
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
